### 2023-02-02 manuscript.tex
reference roadmap/glossary [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/601c8115352e75e7e5f7ba261f24d27cadfa887a.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/601c8115352e75e7e5f7ba261f24d27cadfa887a/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4073799158

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/436f3638b53adb35135c7589db39c8bbbb3d3df9/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/436f3638b53adb35135c7589db39c8bbbb3d3df9}{stain/2022-fdo-paper@436f363}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/601c8115352e75e7e5f7ba261f24d27cadfa887a/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/601c8115352e75e7e5f7ba261f24d27cadfa887a}{stain/2022-fdo-paper@601c811}
on February 2, 2023.
